---
title: "Lab 1"
output: html_document
---

### Loading the data

```{r}
source("http://www.openintro.org/stat/data/cdc.R")
```

### Find the number of cases and variables
```{r}
str(cdc)
```

### Type of variable 'genhlth'
```{r}
str(cdc$genhlth)
```

### Type of variable 'weight'
```{r}
str(cdc$weight)
```

### Type of variable 'smoke100'
```{r}
str(cdc$smoke100)
```

### Summary for the 'gender' variable
```{r}
table(cdc$gender)
```

### Relative Frequency of the 'genhlth' variable
```{r}
genhlth.freq = table(cdc$genhlth)

# compute relative freq by dividing by the total number of cases
genhtlh.relfreq = genhlth.freq / nrow(cdc)

genhtlh.relfreq
```

### Mosaic Plot of Smoking Habits & Gender
```{r}

gender_smokers = table(cdc$gender, cdc$smoke100)

mosaicplot(gender_smokers, shade=TRUE, legend=TRUE)
```

### Subset of people under 23 who have smoked more than 100 cigarettes
```{r}
table(cdc$age <23, cdc$smoke100)
```

### Box Plot of BMI vs genhlth
```{r}
bmi = (cdc$weight / cdc$height ^ 2) * 703
boxplot(bmi ~ cdc$genhlth)

```

### Plot between weight and desired weight
```{r}
plot(log(cdc$wtdesire) ~ log(cdc$weight))
```




